---
title: "assignment4"
author: "Pranav Hari"
date: "25 February 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. A binary source generates digits 1 and 0 randomly with probabilities 0.6 and 0.4, respectively.
  (a). What is the probability that two 1's and three 0's will occur in a five-digit sequence?
  
```{r}
library(distr)
#binomial distribution
B <- Binom(prob=0.6,size=5)
d(B)(2)
```
  b) What is the probability that at least three 1's will occur in a five-digit sequence?
  
```{r}
1-p(B)(2)
```
2. Consider an experiment of tossing a fair coin repeatedly until the coin lands heads the sixth time. Find the probability that it takes exactly 10 tosses.

```{r}
#negative binomial distribution 
A <- Nbinom(prob=0.5,size=6)
d(A)(4)
```
3. An experiment consists of observing the sum of the dice when two fair dice are thrown.
  a) Find the probability that the sum is 7.
  
```{r}
library(prob)
S <- rolldie(2,makespace = TRUE)
Prob(subset(S,X1+X2 == 7))
```
 (b). Find the probability that it will take less than six tosses to throw a 7.
 
```{r}
G <- Geom(prob=0.1666667)
p(G)(5)
```
 (c). Find the probability that it will take more than six tosses to throw a 7.
 
```{r}
1-p(G)(6)
```
4. Let X be a normal distribution with mean 15 and variance 16
  (a). P(9???X???18)
  
```{r}
library(visualize)
pnorm(18,15,4)-pnorm(9,15,4)

```
```{r}
visualize.norm(c(9,18),15,4,section = "bounded")
```
  (b). P(9???X???18|X???15)
  
```{r}
(pnorm(15,15,4)-pnorm(9,15,4))/pnorm(15,15,4)
```
 (c). P(|X???15|???0.6) 
 
```{r}
pnorm(14.4,15,4,lower.tail = TRUE) + pnorm(15.6,15,4,lower.tail = FALSE)
```
Let X be a normal distribution with mean -1 and variance 9.
  (a). Find x such that P(X>x)=0.42.
  
```{r}
qnorm(0.42,-1,3)
```
  (b). Find x such that P(|X+1|<x)=0.45 
  
```{r}
# 2*P(-1 < X < x) = 0.45 because of symmetry
# P(X < x) = 0.45/2 + 0.5 = 0.725
qnorm(0.275,-1,3)

```
